%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{ @{}l C r@{} }
\href{https://github.com/Andrew9317}{\raisebox{-0.05\height}\faGithub \ Andrew9317} &
\Huge{Andrew Hartman}\ &
\href{tel:+12565139447}{\raisebox{-0.05\height}\faMobile \ 256-513-9447} \\
\href{https://www.linkedin.com/in/andrew-hartman-4680a9203/}{\raisebox{-0.05\height}\faLinkedin\ Andrew Hartman} \ &
\href{mailto:andrew.hartman@hartmancoding.com}{\raisebox{-0.05\height}\faEnvelope \ andrew.hartman@hartmancoding.com} \ &
\href{https://hartmancoding.com}{\raisebox{-0.05\height}\faGlobe \ hartmancoding.com} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	KEYWORDS
%----------------------------------------------------------------------------------------
\section{Keywords}
\begin{tabularx}{\linewidth}{|C|C|C|C|}
\textbf{Software Engineer} \ &
\textbf{Embedded Devices} \ &
\textbf{Models \& Sims} \ &
\textbf{Cloud Computing} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{ @{}lCr@{} }
\textbf{Bachelor of Science, Computer Science} & & 2015 - 2018 \\
University of Alabama Huntsville
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages: &  \normalsize{Go, Python, C++, Rust, Javascript, Matlab}\\
Frameworks: & \normalsize{Terraform, Kafka, RabbitMQ, Protobuf, gRPC, Qt, Pandas \& Numpy, React}\\
Tools: & \normalsize{Docker, Kubernetes, AWS (EKS $|$ S3 $|$ ECR), Git, Gitlab \& Jenkins CI/CD, Jira, CMake, Valgrind, Perf, Perforce, SVN}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Founder}&\textbf{Hartman Software Solutions, LLC}&\hfill Current \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Implemented middleware between \textbf{Pixhawk} autopilot and embedded companion computer in \textbf{C++}.
            \item[--] Created flight test GCS for companion computer with \textbf{Qt \& C++}.
            \item[--] Contributed to the opensource GCS \textbf{MissionPlanner}.
            \item[--] Performed post-flight data analysis in \textbf{Python}.
            \item[--] Implemented custom \textbf{Yocto} linux image for use in embedded companion computer.
            \item[--] Created an ABI stable \textbf{C++} lib to support upgrading models without requiring client code to recompile.
            \item[--] Created and maintained language bindings to use \textbf{Go \& Python} with ABI stable \textbf{C++} lib.
            \item[--] \textbf{Mentored} multiple junior and mid-level developers.
        \end{itemize}
        \end{minipage}
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Technical Lead}&\textbf{MTSI}&\hfill Apr 2021 - Jul 2022 \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Designed and implemented \textbf{C++} microservice plugin framework with \textbf{Kafka \& Protobuf} to monitor and correct errant UAV \& Aircraft behavior.
            \item[--] Created and maintained various interfaces to \textbf{hardware sensors} \& \textbf{autopilots}.
            \item[--] Configured \textbf{Gitlab CI/CD} pipelines to rapidly iterate by automating code sanitation and analysis.
            \item[--] Created multiple design documents for use in \textbf{airworithiness certification}.
            \item[--] Maintained \textbf{Docker} images on \textbf{Linux} to run in \textbf{realtime}.
            \item[--] \textbf{Tasked and mentored} team of 3 other software engineers.
        \end{itemize}
        \end{minipage}
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Software Lead}&\textbf{SAIC}&\hfill Oct 2020 - Apr 2021 \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Modified HIMARS / MLRS launcher to be operable remotely via \textbf{UDP, TCP, \& Qt} over radios.
            \item[--] Analyzed and debugged network traffic with \textbf{Wireshark}. 
            \item[--] Cross-compiled binaries between Windows and \textbf{VxWorks}.
            \item[--] \textbf{Tasked and mentored} team of 5 other software engineers.
        \end{itemize}
        \end{minipage}
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Software Engineer}&\textbf{Torch Technologies}&\hfill May 2018 - Oct 2020 \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Set up \textbf{Jenkins CI/CD} jobs to automate code sanition, analysis, and regression tests.
            \item[--] Implemented Python analysis scripts with \textbf{Pandas \& numpy} to analyze simulation data.
            \item[--] Translated IR sensor models and radar fusion algorithms from \textbf{Matlab} to \textbf{C++}.
            \item[--] Created and maintained C++ middleware to allow communication between PATRIOT \textbf{HWIL} and a simulation via \textbf{DIS \& UDP}.
            \item[--] Designed and maintained a cross platform C++ \textbf{Qt} desktop application for data scientists to rapidly iterate on flight test planning.
        \end{itemize}
        \end{minipage}
    }
\\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}