%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{C}
\Huge{Andrew Hartman}\\
\href{tel:+12565139447}{\raisebox{-0.05\height}\faMobile \ 256-513-9447} \\
\href{mailto:andrew.hartman@hartmansoftware.com}{\raisebox{-0.05\height}\faEnvelope \ andrew.hartman@hartmansoftware.com} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	KEYWORDS
%----------------------------------------------------------------------------------------
\section{Keywords}
\begin{tabularx}{\linewidth}{|C|C|C|C|}
\textbf{Software Engineer} \ &
\textbf{Backend} \ &
\textbf{Embedded} \ &
\textbf{Models \& Sims} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages: &  \normalsize{C++, Go, Python}\\
Frameworks: & \normalsize{Kafka, RabbitMQ, FlatBuffers, Protobuf, gRPC, Qt, FastAPI, Postgres, PostGIS}\\
Tools: & \normalsize{Docker, Git, Gitlab \& Jenkins CI/CD, Jira, CMake, Valgrind, Perf, Perforce, SVN}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Experience
\section{Work Experience}
\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Software Consultant}&\textbf{Hartman Software Solutions}&\hfill Current \\[3.75pt]
    \multicolumn{3}{p{7.3in}}{
        \vspace{0mm}
        \footnotesize{
            \textbf{Responsibilities:} Read multiple messages from different vendor hardware 
            (\textbf{ARINC-429, MIL-STD-1553, etc}) and translate them to a common \textbf{Protobuf} format. 
            The messages were then compressed with \textbf{ZStd} and made available to send to different sinks 
            (\textbf{MQTT, Kafka, TCP, etc}) based on configuration.
        }
    } \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \small{
        \begin{minipage}[t]{\linewidth}
        \vspace{0mm}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt, align=right]
            \item[--] Architected and implemented a core library in modern \textbf{C++23} to provide common interfaces to collect messages from multiple hardware vendor APIs.
            \item[--] Optimized main message collection hotpath, resulting in \textbf{82\%} increased throughput.
            \item[--] Implemented wrapper around \textbf{Opentelemetry} to compress and write logs, traces, and metrics to disk with \textbf{ZStd}, stream to an \textbf{OTLP} collector, or output in plaintext to the console.
            \item[--] Implemented robust \textbf{CICD} pipeline on legacy \textbf{C++03} libraries, exposing and fixing \textbf{1000+} warnings, static-analysis findings, and sanitizer findings.
            \item[--] Identified and fixed multiple data-race and threading bugs.
            \item[--] Set up multiple dashboards and graphs to get insights from \textbf{OpenTelemetry} via \textbf{Signoz}
            \item[--] \textbf{Mentored} multiple junior and mid-level developers.
        \end{itemize}
        \end{minipage}
        }
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Sr. Software Engineer}&\textbf{Rebellion Defense}&\hfill Jul 2022 - Oct 2023 \\[3.75pt]
    \multicolumn{3}{p{7.3in}}{
        \vspace{0mm}
        \footnotesize{
            \textbf{Responsibilities:} Design and create the foundation for a cloud based modeling \& simulation platform.
            I was tasked with architecting and leading the development of the framework that controlled the models, data flow, timing, and more.
        }
    } \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \small{
        \begin{minipage}[t]{\linewidth}
        \vspace{0mm}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Architected and implemented an ABI stable \textbf{C++} lib reducing time to implement new language support by \textbf{90\%} and supporting simulation upgrades without requiring clients to recompile their code.
            \item[--] Architected and implemented language bindings with the above lib to enable \textbf{Go \& Python} simulation models.
            \item[--] Implemented \textbf{OpenTelemetry} instrumentation interface for logging, tracing, and metrics in the \textbf{C++, Go, \& Python} codebases.
            \item[--] Optimized \textbf{OpenTelemetry gRPC} exporters to be async resulting in \textbf{198\%} increased throughput.
            \item[--] Set up multiple dashboards and graphs to get insights from \textbf{OpenTelemetry} via \textbf{AWS OpenSearch}
            \item[--] Architected and implemented multiple backend \textbf{REST} api layers using Python's \textbf{FastAPI} framework.
            \item[--] Migrated prototype / legacy \textbf{Python} codebase to \textbf{Go} resulting in 102\% performance increase.
            \item[--] Migrated \textbf{Postgres} database / queries to use \textbf{PostGIS} resulting in a 61\% faster response time.
            \item[--] \textbf{Tasked and mentored} multiple junior and mid-level developers.
        \end{itemize}
        \end{minipage}
        }
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Software Lead}&\textbf{MTSI}&\hfill Apr 2021 - Jul 2022 \\[3.75pt]
    \multicolumn{3}{p{7.3in}}{
        \vspace{0mm}
        \footnotesize{
            \textbf{Responsibilities:} Partner with NASA to design and create a framework that enabled AI \& ML on safety critical devices. 
            Our focus was enabling autonomy on drones to allow certification of non-human-in-the-loop systems. 
            Essentially, by running the framework on a drone you would be cleared to fly without an operator and could have the autonomous system take full control completely outside of radar range. 
        }
    } \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \small{
        \begin{minipage}[t]{\linewidth}
        \vspace{0mm}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Architected and implemented a robust \textbf{C++} microservice framework utilizing \textbf{Kafka and Protobuf} to actively monitor and rectify erroneous UAV and Aircraft behavior.
            \item[--] Selected on-vehicle hardware and software components to align with the defined architecture and product offerings.
            \item[--] Architected and implemented diverse interfaces to hardware sensors and autopilots in \textbf{C++}, ensuring seamless integration and data exchange.
            \item[--] Developed clear company-wide engineering strategies for observability, testing, and code quality.
            \item[--] Migrated legacy \textbf{C} libraries into modern \textbf{C++20} libraries.
            \item[--] Implemented custom \textbf{Yocto} linux image for use in embedded companion computer.
            \item[--] Architected and implemented an in-flight status monitor for flight testing using \textbf{Qt}.
        \end{itemize}
        \end{minipage}
        }
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Software Lead}&\textbf{SAIC}&\hfill Oct 2020 - Apr 2021 \\[3.75pt]
    \multicolumn{3}{p{7.3in}}{
        \vspace{0mm}
        \footnotesize{
            \textbf{Responsibilities:} Modify the MLRS / HIMARS launcher to be operable remotely for range safety while testing experimental munitions. 
        }
    } \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \small{
        \begin{minipage}[t]{\linewidth}
        \vspace{0mm}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Architected and implemented modifications of HIMARS / MLRS launcher to be operable remotely via \textbf{UDP, TCP, \& Qt} over radios.
            \item[--] Worked closely with the customer and systems team to ensure the \textbf{UX} was intuitive.
            \item[--] Concentrated on reducing operator cognitive load regarding latency and launcher state.
            \item[--] Optimized and translated old \textbf{C++03} code to modern \textbf{C++17} equivalent.
            \item[--] \textbf{Tasked and mentored} team of 4 other software engineers.
        \end{itemize}
        \end{minipage}
        }
    }
\\
\\
\end{tabularx}

\begin{tabularx}{\linewidth}{
    >{\hsize=0.8\hsize}X
    >{\hsize=1.2\hsize}C
    >{\hsize=1.0\hsize}X
    }
    \textbf{Software Engineer}&\textbf{Torch Technologies}&\hfill May 2018 - Oct 2020 \\[3.75pt]
    \multicolumn{3}{p{7.3in}}{
        \vspace{0mm}
        \footnotesize{
            \textbf{Responsibilities:} Extend a high-fidelity PATRIOT simulation to work in realtime with an HWIL ICC and create a flight test planning tool for hypersonic missiles with a focus on satellite sensor participation.
        }
    } \\[3.75pt]
    \multicolumn{3}{@{}l@{}}{
        \small{
        \begin{minipage}[t]{\linewidth}
        \vspace{0mm}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Architected and implemented Python analysis scripts with \textbf{Pandas \& numpy} to analyze simulation data.
            \item[--] Translated IR sensor models and radar fusion algorithms from \textbf{Matlab} to \textbf{C++}.
            \item[--] Architected and implemented a cross platform C++ \textbf{Qt} desktop application for data scientists to rapidly iterate on flight test planning for hypersonic missiles.
            \item[--] Worked closely with the customer regarding \textbf{UX} to ensure the UI was intuitive.
            \item[--] Set up \textbf{Jenkins CI/CD} jobs to automate code sanition, analysis, and regression tests.
            \item[--] Debugged C++ middleware to allow communication between PATRIOT \textbf{HWIL} and a simulation via \textbf{DIS \& UDP}.
        \end{itemize}
        \end{minipage}
        }
    }
\\
\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{ @{}lCr@{} }
\textbf{Bachelor of Science, Computer Science} & & 2015 - 2018 \\
University of Alabama Huntsville
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
